### 2011-11-07 doc/pldi2012/circuit.tex

%The declarations for the three subtasks are shown on lines 42-51.  
The  {\tt calc\_new\_currents} task reads and writes the wires subregion, 
the nodes subregion, and the ghost node region for its piece.
The {\tt distribute\_charge} subtask turns things around, reading the piece's 
wires subregion and updating all nodes those wires touch.  However,
rather than requesting the ability to read and write the nodes (which would
require serialization of these tasks for correctness), the task declares that
it will use reorderable {\em reduction} operations and that the coherence requirement
is {\em atomic} rather than exclusive access. The final task is 
{\tt update\_voltages}, which writes the shared and private nodes for a piece
and reads the results of the previous task's reductions.

@@

Since a region relationship can have
fields with types that refer its own fields' regions, it is often not possible
to assign fields one at a time without violating the type checking rules.
The simultaneous assignment operator asks the type checker only to ensure
that fields have the correct types after all the fields are updated.  
Lines 32 and 33 illustrate a simultaneous
assignment to update a {\tt CircuitPiece} region relationship.

>>>>

%The declarations for the three subtasks are shown on lines 42-51.  
The  {\tt calc\_new\_currents} task reads and writes the wires subregion, 
the nodes subregion, and the ghost node region for its piece.
The {\tt distribute\_charge} subtask is a different phase that reads the piece's 
wires subregion and updates all nodes those wires touch.  However,
rather than requesting the ability to read and write the nodes (which would
require serialization of these tasks for correctness), the task declares that
it will use reorderable {\em reduction} operations and that the coherence requirement
is {\em atomic} rather than exclusive access. The final task is 
{\tt update\_voltages}, which writes the shared and private nodes for a piece
and reads the results of the previous task's reductions.

@@

Since a region relationship can have
fields with types that refer to its own fields' regions, it is often not possible
to assign fields one at a time without violating the type checking rules.
The simultaneous assignment operator asks the type checker only to ensure
that fields have the correct types after all the fields are updated.  
Lines 32 and 33 illustrate a simultaneous
assignment to update a {\tt CircuitPiece} region relationship.
